The symmetry of partner modelling

### 2016-02-04 mutual-modeling.tex
Split section 3 and created a new section 'Methodological Issues'

Measuring \Model{A}{B}{X} is methodologically difficult. We
discriminate two steps, first to capture \model{A}{B}{X} and then to
estimate \Model{A}{B}{X}.

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$
        what he/she believes about what $B$ knows, feels, intends to do, etc.
        This raises obvious methodological concerns since such a question
        triggers a modelling process beyond what would naturally occur. To avoid
        this bias, one can estimate mutual modelling after task completion.
        Then, the obvious drawback are memory losses and by post-hoc
        reconstruction.  The first method was used in study 2 and the second one
        in the other studies. Another option would be to rely on external
        behavioural metrics like eye-tracking: we hypothesise for instance that
        the fixation time reflects the efforts engaged by the human to
        understand, hence, model, the others. Such an approach has however not
        been investigated in the presented studies.

    \item {\bf Estimating \Model{A}{B}{X}}: Once \model{A}{B}{X} is captured, we
        need to access the reference model \refmodel{B}{X} to estimate its
        \emph{accuracy}. Since we can only indirectly access it via what $B$
        reports (\ie \model{B}{B}{X}), accuracy can be estimated in 2 ways:

@@

>>>>

\section{Methodological Issues}

Since a mental model is not directly observable,  the study of mutual modelling is methodologically difficult. How can we for instance measure \Model{A}{B}{X}. We proceed in two steps, first to capture \model{A}{B}{X} and then to
estimate \Model{A}{B}{X}.

{\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$
        what he/she believes about what $B$ knows, feels, intends to do, etc.
        This raises obvious methodological concerns since such a question
        triggers a modelling process beyond what would naturally occur. To avoid
        this bias, one can estimate mutual modelling after task completion.
        Then, the obvious drawback are memory losses and by post-hoc
        reconstruction.  The first method was used in study 2 and the second one
        in the other studies. Another option would be to rely on external
        behavioural metrics like eye-tracking: we hypothesise for instance that
        the fixation time reflects the efforts engaged by the human to
        understand, hence, model, the others. Such an approach has however not
        been investigated in the presented studies.

    {\bf Estimating \Model{A}{B}{X}}: Once \model{A}{B}{X} is captured, we
        need to access the reference model \refmodel{B}{X} to estimate its
        \emph{accuracy}. Since we can only indirectly access it via what $B$
        reports (\ie \model{B}{B}{X}), accuracy can be estimated in 2 ways:

@@

Our method for investigating mutual modelling is observe the variations of  accuracy that result from variations of external parameters that appear as variable in the formula presented in the previous section: the accuracy should for go down if we increase the cost of grounding acts and goes up if we increase the grounding criterion (the necessity to build a shared understanding). One way to produce these variations is what CSCW,researchers have called
``awareness tools'', \ie functionalities that inform $A$ is about $B$'s actions
that A could not directly perceive because $B$ was working on a different subset
of the virtual space. Different awareness tools are used in the following studies as methodological tricks  to manipulate experimentally the  mutual modelling activity.
